---
title: "antaresViz"
author: "Jalal-Edine ZAWAM"
date: "20 juillet 2018"
output:
    html_document:
      number_sections: yes
      toc: yes
---

```{r param, echo=FALSE}

#param of all examples
pathStudy <- "E:\\ANTARES\\Exemple_antares\\2_exemple_etudes_importantes\\TYNDP\\ST2030\\ST2030"

pathStudyL <- "E:\\ANTARES\\Exemple_antares\\3_petit_exemple\\PackagesR\\Test_packages_R_602"

```


# Introduction

`antaresViz` is on [CRAN](https://cran.r-project.org/web/packages/antaresViz/index.html). This package can help you to visualize results from the open source software ANTARES, more information about ANTARES [here](https://github.com/AntaresSimulatorTeam/Antares_Simulator). 

This documentation will present some new examples for `antaresViz` and also how to use R, data.table and RStudio. 

# How to represent the generation mix for each country?

Here we have to use the `prodStack` function.

```{r prodStackHelp, eval=FALSE}
#you can visualize prodStack help with this command on RStudio
#you will find some examples
??prodStack

```

## Generation mix for hourly data

```{r importHourlyData, echo=TRUE}
suppressMessages(library(antaresViz))
#pathStudy : path to my study 
suppressWarnings(opts <- setSimulationPath(pathStudy,-1))
myData <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE))

prodStack(myData, interactive = FALSE, areas = "fr", dateRange = c("2018-07-01", "2018-07-05"))

#prodStack can also be an interactive application, a user can set this behaviour in two ways: 
#1. do not set the "interactive" parameter (by default, interactive is set to TRUE)
#2. set "interactive" parameter to TRUE

#run it in your console
#prodStack(myData, areas = "fr", dateRange = c("2018-07-01", "2018-07-05"))

#run it in your console
#prodStack(myData, interactive = TRUE, areas = "fr", dateRange = c("2018-07-01", "2018-07-05"))

```


One can also include `prodStack` in a shiny app like for the adequacy French report 
[bpnumerique](http://bpnumerique.rte-france.com/), tab "Analyse detaillee".

## Generation mix for daily, weekly or monthly data
```{r importDWMData, echo=TRUE}
suppressMessages(library(antaresViz))
#pathStudy : path to my study 
suppressWarnings(opts <- setSimulationPath(pathStudy,-1))
myDataD <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE, timeStep = "daily"))
myDataW <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE, timeStep = "weekly"))
myDataM <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE, timeStep = "monthly"))

dataRangeEx <- c("2018-06-25", "2018-07-05")
prodStack(myDataD, interactive = FALSE, areas = "fr", dateRange = dataRangeEx)
prodStack(myDataW, interactive = FALSE, areas = "fr", dateRange = dataRangeEx)
prodStack(myDataM, interactive = FALSE, areas = "fr", dateRange = c("2018-05-01", "2018-09-30"))

#try to plot weekly data for one week in your console 
#try to plot monthly data for one month in your console 
#prodStack(myDataW, interactive = FALSE, areas = "fr", dateRange = c("2018-07-01", "2018-07-05"))
#prodStack(myDataM, interactive = FALSE, areas = "fr", dateRange = c("2018-05-01", "2018-05-30"))

```

## Generation mix for annual data
```{r importAnnualData, echo=TRUE}
suppressMessages(library(antaresViz))
#pathStudy : path to my study 
suppressWarnings(opts <- setSimulationPath(pathStudy,-1))
myDataA <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE, timeStep = "annual"))

prodStack(myDataA, interactive = FALSE, areas = "fr")
```

# How to represent LOLD and ENS for each country? 

## With plot it's easy 
`plot` help you to visualize a time series and can also help you to visualize LOLE and ENS. 

```{r plotLOLE, echo=TRUE}
suppressMessages(library(antaresViz))
#pathStudy : path to my study 
suppressWarnings(opts <- setSimulationPath(pathStudy,-1))
#get only some areas 
myAreas <- c("fr", "fi", "be")
myDataH <- suppressWarnings(readAntares(areas = myAreas, showProgress = FALSE))

#one country and one variable
plot(myDataH, interactive = FALSE, elements = "fr", variable = "UNSP. ENRG")
#one country and several variables
plot(myDataH, interactive = FALSE, elements = "fr", variable = c("UNSP. ENRG", "LOLD", "LOLP"))
#several countries and one variable
plot(myDataH, interactive = FALSE, elements = c("fr", "fi", "be"), variable = c("UNSP. ENRG"))
#several countries and several variables
plot(myDataH, interactive = FALSE, elements = c("fr", "fi", "be"), variable = c("UNSP. ENRG", "LOLD", "LOLP"))
#one country and several variables but with monotone
plot(myDataH, interactive = FALSE, elements = "be", variable = c("WIND", "SOLAR"), type = "monotone")

```

## Other possibilities

`plot` can be used with `type` "barplot", "density", "cdf" or "heatmap" to visualize some variables like "LOLD". 

`prodStack` can also be used to visualize a lack of production. 


```{r prodStackLOLE, echo=TRUE}
suppressMessages(library(antaresViz))
#pathStudy : path to my study 
suppressWarnings(opts <- setSimulationPath(pathStudy,-1))
#get only some areas 
myAreas <- c("fr", "fi", "be")
myDataH <- suppressWarnings(readAntares(areas = myAreas, showProgress = FALSE))

dateWithENS <- myDataH[LOLD >0 , time][1]
dateWithENS
firstDate <- dateWithENS - 60*60*24
lastDate <- dateWithENS + 60*60*24
prodStack(myDataH, interactive = FALSE, areas = "fr", dateRange = c(firstDate, lastDate))

```

## For several simulations
```{r plotLoleSims, echo=TRUE}
suppressMessages(library(antaresViz))
#pathStudy : path to my study 
suppressWarnings(opts <- setSimulationPath(pathStudy,-1))
#only some variables
varToGet <- c("UNSP. ENRG", "LOLD", "LOLP")
myDataS1 <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE, select = varToGet))
suppressWarnings(opts <- setSimulationPath(pathStudy,-2))
myDataS2 <- suppressWarnings(readAntares(areas = "fr", showProgress = FALSE, select = varToGet))

#one simulation and one variable
plot(myDataS1, interactive = FALSE, elements = "fr", variable = "UNSP. ENRG")
plot(myDataS2, interactive = FALSE, elements = "fr", variable = "UNSP. ENRG")

#plot in the same graph the two variables
myDataS1[, unspEnrgS1 := `UNSP. ENRG`]
myDataS1[, unspEnrgS2 := myDataS2$`UNSP. ENRG`]
plot(myDataS1, interactive = FALSE, elements = "fr", variable = c("unspEnrgS1", "unspEnrgS2"))

```
