---
title: "antaresRead 2.1.0 More Examples"
author: "Jalal-Edine ZAWAM"
date: "22 mars 2018"
output:
    html_document:
      number_sections: yes
      toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r param, echo=FALSE}

#param of all examples
pathStudy<-"E:\\ANTARES\\Exemple_antares\\2_exemple_etudes_importantes\\TYNDP\\ST2030\\ST2030"

```


# Areas and Links

## How to import daily, weekly, monthly and annual data ? 

Import daily data  

```{r importDailyData, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myData<-suppressWarnings(readAntares(areas = "fr", links = "all", timeStep = "daily", showProgress = FALSE))
```

Check your import 

```{r CheckDailyData, echo=TRUE}

length(myData$areas$time)
```


Import weekly data  

```{r importWeeklyData, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myData<-suppressWarnings(readAntares(areas = "fr", links = "all", timeStep = "weekly", showProgress = FALSE))
```

Check your import 

```{r CheckWeeklyData, echo=TRUE}

length(myData$areas$time)
```

Import monthly data  

```{r importMonthlyData, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myData<-suppressWarnings(readAntares(areas = "fr", links = "all", timeStep = "monthly", showProgress = FALSE))
```

Check your import 

```{r CheckMonthlyData, echo=TRUE}

length(myData$areas$time)
```

Import annual data  

```{r importAnnualData, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myData<-suppressWarnings(readAntares(areas = "fr", links = "all", timeStep = "annual", showProgress = FALSE))
```

Check your import 

```{r CheckAnnualData, echo=TRUE}

length(myData$areas$time)
```


## How to write some variables in a csv file ? 

Import your data 

```{r importExCsv, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myData<-suppressWarnings(readAntares(areas = "all", links = "all", showProgress = FALSE, select = c("economy", "FLOW LIN.", "CONG. PROB +", "CONG. PROB -")))
```

Write some variables 


```{r writeCsv, echo=TRUE}

write.csv2(file="myFileArea.csv", myData$areas[area=="fr",])
write.csv2(file="myFileLink.csv", myData$links[link=="0_pump_daily - fr", ])
```

## How can I know the type and class of my ANTARES object ? 

If you import areas and links you will get an antaresDataList. You can find more information about antareDataList with the help of the function `as.antaresDataList` in the package antaresRead. 
If you import only areas or links you will get an antaresDataTable. An antaresDataTable is also a data.table and a data.frame. If you don't know what's a data.table you can find more information [here](https://github.com/Rdatatable/data.table/wiki). If you don't know what's a data.frame you can find more information [here](http://www.r-tutor.com/r-introduction/data-frame). We advise you to use the data.table features. 

```{r classList, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myDataL<-suppressWarnings(readAntares(areas = "all", links = "all", showProgress = FALSE, select = c("economy")))

myDataTA<-suppressWarnings(readAntares(areas = "all", showProgress = FALSE, select = c("economy")))

myDataTL<-suppressWarnings(readAntares(links = "all", showProgress = FALSE))

```

Get the class and type of your object


```{r getClass, echo=TRUE}
class(myDataL)
typeof(myDataL)

class(myDataTA)
typeof(myDataTA)

class(myDataTL)
typeof(myDataTL)
```

# Links 

## How to get the value of maximum flow capacity for a link ? 

Import your data 
```{r importCapaLink, echo=TRUE}
library(antaresRead)
#pathStudy : path to my study 
suppressWarnings(opts<-setSimulationPath(pathStudy,-1))
myData<-suppressWarnings(readAntares(links = "all", linkCapacity = TRUE, showProgress = FALSE))
```

Get the maximum flow capacity for a link


```{r maximumFlow, echo=TRUE}
max(myData[link=="0_pump_daily - fr", transCapacityDirect])
max(myData[link=="0_pump_daily - fr", transCapacityIndirect])
```